Influence of anomalous perpendicular transport on linear tearing mode dynamics in tokamak plasmas

### 2022-01-27 Research/LinearTearingModeTheory/Version2/Paper2.tex
Latest version

\begin{abstract}
The analysis of a previous paper [A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006)] that maps out all of the
two-fluid response regimes of a  linear tearing layer interacting with an externally generated resonant magnetic perturbation, in a large aspect-ratio tokamak plasma,  is generalized to
take into account realistic levels of perpendicular particle transport. A new response-regime map is obtained that differs substantially, in many
respects, from the old one. The improved analysis is first employed to find all of the two-fluid growth-rate regimes of a non-interacting low-mode-number tearing mode in a large aspect-ratio tokamak plasma. 
The analysis is then used to determine the scaling of the error-field penetration threshold with machine
parameters in large aspect-ratio, ohmically heated, tokamak plasmas. A number of penetration regimes are found in which the threshold scales as $n^{1/2}$, where $n$ is the line-averaged
electron number density. A similar scaling has been reported in some experiments. 
\end{abstract}

@@

It is well known that single-fluid, resistive magnetohydrodynamics (MHD) offers a very poor description of
tearing mode dynamics in tokamak plasmas. 
For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion flows to some extent,
necessitating a two-fluid treatment.\cite{ara} Moreover, resistive-MHD does not take  the important {\em ion sound radius lengthscale}, below which electron and ion dynamics are further decoupled, 
into account.\cite{drake,wal} Previously, Cole \& Fitzpatrick\,\cite{cole} used the four-field model
of Fitzpatrick \& Waelbroeck\,\cite{fw} (which is based on the original four-field model of Hazeltine, et al.\cite{haz}) 
to determine the two-fluid response of a linear tearing layer to an externally generated, 
resonant magnetic perturbation  in a large aspect-ratio tokamak plasma. However, the treatment of Cole \& Fitzpatrick fails to take into account the
 anomalously large perpendicular  particle diffusivity  present in tokamak plasmas. The
aim of this paper is to correct this deficiency.

This paper is organized as follows. After some preliminary analysis in Sect.~\ref{sect1}, our fundamental four-field resonant
plasma response model is introduced in Sect.~\ref{sfour}. This model is a slightly improved version of the model derived in Ref.~\onlinecite{fw} that takes the thermal force into account. The model is converted into a set of linear layer equations in
Sect.~\ref{layer}. These layer equations are then solved in Sect.~\ref{linear} in order to map out all of the linear response regimes
of a resonant layer to an externally generated resonant magnetic perturbation in a large aspect-ratio tokamak plasma. In Sect.~\ref{stab}, we reuse the analysis of Sect.~\ref{linear} to map out all
of the growth-rate regimes for a low-mode-number (but not $m=1$) tearing mode in a large aspect-ratio tokamak plasma. Finally,
in Sect.~\ref{error}, we employ the results of Sect.~\ref{linear} to determine the scaling of the error-field penetration threshold with machine parameters
 in large aspect-ratio, ohmically heated, tokamak plasmas.

@@

In the so-called {\em outer region}\/ (i.e., everywhere in the plasma
apart from the resonant layer), the perturbed helical magnetic flux, $\delta\psi(r,t)$, satisfies the
{\em cylindrical tearing mode equation}:\cite{wes}
\begin{equation}\label{e3}
\frac{\partial^2\delta\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\delta\psi}{\partial r}-\frac{m^2}{r^2}\,\delta\psi - \frac{J_z'\,\delta\psi}{r\,(1/q-n/m)}=  0,
\end{equation}
where 
$J_z(r)= R_0\,\mu_0\,j_z(r)/B_z$,
and $j_z(r)$ is the equilibrium `toroidal' current density. Here, $'\equiv d/dr$. In general, the solution of Eq.~(\ref{e3}) that satisfies physical
boundary conditions at the magnetic axis and the plasma boundary is such that $\delta\psi$ is continuous
across the resonant surface, whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity of
 $\partial\delta\psi/\partial r$ across the resonant surface is indicative of the presence of a helical current
 sheet at the surface.  The complex quantity ${\mit\Psi}_s(t)= \delta\psi(r_s,t)$ determines the amplitude
 and phase of the reconnected helical magnetic flux at the resonant surface, whereas the complex quantity\,\cite{rf1993}
 \begin{equation}
{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \delta\psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
\end{equation}
parameterizes the amplitude and phase of the helical current sheet flowing at the surface. The solution of
the cylindrical tearing mode equation in the outer region, in the presence of an externally generated, resonant magnetic perturbation 
of the same helicity as the tearing mode, leads to the relation\,\cite{rf1993,fkr}
\begin{equation}\label{e110}
{\mit\Delta\Psi}_s= {\mit\Delta}_s'\,{\mit\Psi}_s + (-{\mit\Delta}_s')\,{\mit\Psi}_v,
\end{equation}
where ${\mit\Delta}_s'$ is a real dimensionless quantity known as the {\em tearing stability index}. Moreover,
${\mit\Psi}_v$ is the so-called {\em vacuum flux}, and is defined as the reconnected magnetic flux
that would be driven at the resonant surface by the resonant magnetic perturbation were the
plasma intrinsically tearing stable (i.e., ${\mit\Delta}_s' <0$), and were there no current sheet at the resonant surface
(i.e., ${\mit\Delta\Psi}_s=0$).

@@

\subsection{Fundamental Equations}
The four-field model takes the form:\cite{fw}
\begin{align}
\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\left(\frac{\tau}{1+\tau}\right)(1+\lambda_e)\,[N,\psi]
+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{1}{2\,(1+\tau)}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \frac{N}{1+\tau}\right), \\[0.5ex]
\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\psi] +\hat{d}_\beta^{\,2}\,[J,\psi]
+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
\end{align}
Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, 
$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
diffusivity at the resonant surface. 
Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
$\lambda_e=0.71\,\eta_e/(1+\eta_e)$. Finally,\cite{fw}
\begin{equation}
\hat{D}_\perp \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e}{1+\eta_e}\,\frac{\tau}{1+\tau}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i}{1+\eta_i}\,\frac{1}{1+\tau}\,\hat{\chi}_{\perp\,i}\right),
\end{equation}
where $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, and $\chi_{\perp\,e,i}$ is the (anomalous)
perpendicular electron/ion  energy diffusivity in the vicinity of the resonant surface. 
Note that Cole \& Fitzpatrick (2006) neglects the contribution of $\chi_{\perp\,e,i}$ to the perpendicular particle
diffusivity, $D_\perp$, leading to an anomalously small estimate for $D_\perp$. It is this deficiency that we aim to
correct in the present paper.

@@

\subsection{Derivation of Linear Layer Equations}
In accordance with Eqs.~(\ref{e23})--(\ref{e28}), let us write
\begin{align}\label{e31}
\psi(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\left(\frac{1+\tau}{\tau}\right)\!\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel + \left(\frac{1+\tau}{\tau}\right)\!\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e36}
\end{align}
where $\zeta=m\,\theta-n\,\varphi$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
Substituting Eqs.~(\ref{e31})--(\ref{e36}) into Eqs.~(\ref{e16})--(\ref{e21}), 
 and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear equations:
\begin{align}\label{e37}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\!\left(\frac{\tau}{1+\tau}\right)\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}\nonumber\\[0.5ex]
&\phantom{=} + S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e40}
\end{align}
Here, 
$\tau_H = L_s/(m\,V_A)$ 
is the  hydromagnetic time, 
$\omega_E =(m/r_s)\,V_E(r_s)$
  the 
 ${\bf E}\times {\bf B}$ frequency, 
$\omega_{\ast\,e} = -[\tau/(1+\tau)](m/r_s)V_\ast(r_s)$
the 
   electron diamagnetic
frequency,
$\omega_{\ast\,i} =[1/(1+\tau)](m/r_s)V_\ast(r_s)$
 the  ion diamagnetic
frequency, 
$S=\tau_R/\tau_H$
 the  Lundquist number, 
$\tau_R = \mu_0\,r_s^{\,2}/\eta_\parallel$
 the
 resistive diffusion time, 
$\tau_\varphi
= r_s^{\,2}/\chi_\varphi$
the  toroidal momentum confinement time, and 
$\tau_\perp = r_s^{\,2}/D_\perp$.
  Furthermore, $P_\varphi = \tau_R/\tau_\varphi$ and $P_\perp = \tau_R/\tau_\perp$ are magnetic Prandtl numbers.

 Let us define the stretched radial variable $X = S^{1/3}\,\hat{x}$.
Assuming that $X\sim{\cal O}(1)$ in the layer (i.e., assuming that the layer thickness is roughly of order $S^{-1/3}\,r_s$),
and making use of the fact that $S\gg 1$ in conventional tokamak plasmas,  Eqs.~(\ref{e37})--(\ref{e40}) reduce to the following
set of linear layer equations:\,\cite{cole}
\begin{align}\label{e43}
-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_{e}]\,\tilde{\psi}&= - {\rm i}\,X\left[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}\right] + \frac{d^{\,2}\tilde{\psi}}{d X^2},\\[0.5ex]
-{\rm i}\,(Q-Q_E -Q_{i})\,\frac{d^{\,2}\tilde{\phi}}{dX^2}&= - {\rm i}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^2}+ P_\varphi\,\frac{d^{\,4}}{dX^4}\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(Q-Q_E)\tilde{N} &= - {\rm i}\,Q_{e}\,\tilde{\phi} - {\rm i}\,c_\beta^{\,2}\,X\,\tilde{V}  - {\rm i} \,D^{2}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^{2}}
+ P_\perp\,\frac{d^{\,2} \tilde{N}}{dX^{2}},\\[0.5ex]
 -{\rm i}\,(Q-Q_E)\,\tilde{V} &= {\rm i}\,Q_{e}\,\tilde{\psi} - {\rm i}\,X\,\tilde{N} + P_\varphi\,\frac{d^{\,2}\tilde{V}}{dX^{2}}.\label{e46}
\end{align}
Here, $Q=S^{\,1/3}\,\omega\,\tau_H$, $Q_E = S^{\,1/3}\,\omega_E\,\tau_H$, $Q_{e,i} = S^{\,1/3}\,\omega_{\ast\,e,i}\,\tau_H$,
and $D = S^{\,1/3}\,[\tau/(1+\tau)]^{1/2}\,\hat{d}_\beta$.

\subsection{Asymptotic Matching}
The  linear layer equations, (\ref{e43})--(\ref{e46}), possess tearing parity solutions
characterized by the symmetry $\tilde{\psi}(-X)=\tilde\psi(X)$, $\tilde{\phi}(-X)=-\tilde{\phi}(X)$, 
$\tilde{N}(-X)= - \tilde{N}(X)$, $\tilde{V}(-X)=\tilde{V}(X)$. If we assume that
the asymptotic behavior of the tearing parity layer solutions is such that 
\begin{equation}\label{e47}
\tilde{\psi}\rightarrow  \psi_0\!\left[1+ \frac{\hat{\mit\Delta}}{2}\,|X| + {\cal O}(X^2)\right]
\end{equation}
as $|X|\rightarrow\infty$, where $\psi_0$ is an arbitrary constant, then asymptotic matching to the outer solution yields
\begin{equation}\label{e48}
{\mit\Delta\Psi}_s= S^{1/3}\,\hat{\mit\Delta}\,\,{\mit\Psi}_s.
\end{equation}

@@

>>>>

\begin{abstract}
The analysis of a previous paper [A.~Cole, and R.~Fitzpatrick, Phys.\ Plasmas {\bf 13}, 032503 (2006)] that maps out all of the
two-fluid response regimes of a  linear tearing layer interacting with an externally generated resonant magnetic perturbation, in a large aspect-ratio tokamak plasma,  is generalized to
take into account realistic levels of perpendicular particle transport. A new response-regime map is obtained that differs substantially, in many
respects, from the old one. The improved analysis is first employed to find all of the two-fluid growth-rate regimes of a non-interacting low-mode-number tearing mode in a large aspect-ratio tokamak plasma. 
The analysis is then used to determine the scaling of the error-field penetration threshold with machine
parameters in large aspect-ratio tokamak plasmas. 
\end{abstract}

@@

It is well known that single-fluid, resistive magnetohydrodynamics (MHD) offers a very poor description of
tearing mode dynamics in tokamak plasmas. 
For instance, the strong {\em diamagnetic}\/ flows present in such plasmas decouple the electron and ion flows to some extent,
necessitating a two-fluid treatment.\cite{ara} Moreover, resistive-MHD does not take  the important {\em ion sound radius} lengthscale, below which electron and ion dynamics are further decoupled, 
into account.\cite{drake,wal} Previously, Cole \& Fitzpatrick\,\cite{cole} used the four-field model
of Fitzpatrick \& Waelbroeck\,\cite{fw} (which is based on the original four-field model of Hazeltine, et al.\cite{haz}) 
to determine the two-fluid response of a linear tearing layer to an externally generated, 
resonant magnetic perturbation  in a large aspect-ratio tokamak plasma. However, the treatment of Cole \& Fitzpatrick fails to take into account the
 anomalously large perpendicular  particle diffusivity  present in tokamak plasmas. The
aim of this paper is to correct this deficiency.

This paper is organized as follows. After some preliminary analysis in Sect.~\ref{sect1}, our fundamental four-field resonant
plasma response model is introduced in Sect.~\ref{sfour}. This model is a slightly improved version of the model derived in Ref.~\onlinecite{fw} that takes the thermal force into account. (The thermal force merely gives rise to an additional term  in the perpendicular electron fluid velocity that scales as the electron temperature gradient.) The model is converted into a set of linear layer equations in
Sect.~\ref{layer}. These layer equations are then solved in Sect.~\ref{linear} in order to map out all of the linear response regimes
of a resonant layer to an externally generated, resonant magnetic perturbation in a large aspect-ratio tokamak plasma. In Sect.~\ref{stab}, we reuse the analysis of Sect.~\ref{linear} to map out all
of the growth-rate regimes for a low-mode-number (but not $m=1$) tearing mode in a large aspect-ratio tokamak plasma. Finally,
in Sect.~\ref{error}, we employ the results of Sect.~\ref{linear} to determine the scaling of the error-field penetration threshold with machine parameters
 in large aspect-ratio tokamak plasmas.

@@

In the so-called {\em outer region}\/ (i.e., everywhere in the plasma
apart from the resonant layer), the perturbed helical magnetic flux, $\delta\psi(r,t)$, satisfies the
{\em cylindrical tearing mode equation}:\cite{wes}
\begin{equation}\label{e3}
\frac{\partial^2\delta\psi}{\partial r^2} + \frac{1}{r}\,\frac{\partial\delta\psi}{\partial r}-\frac{m^2}{r^2}\,\delta\psi - \frac{J_z'\,\delta\psi}{r\,(1/q-n/m)}=  0,
\end{equation}
where 
$J_z(r)= R_0\,\mu_0\,j_z(r)/B_z$,
and $j_z(r)$ is the equilibrium `toroidal' current density. Here, $'\equiv d/dr$. In general, the solution of Eq.~(\ref{e3}) that satisfies physical
boundary conditions at the magnetic axis and the plasma boundary is such that $\delta\psi$ is continuous
across the resonant surface, whereas $\partial\delta\psi/\partial r$ is discontinuous. The discontinuity of
 $\partial\delta\psi/\partial r$ across the resonant surface is indicative of the presence of a helical current
 sheet at the surface.  The complex quantity ${\mit\Psi}_s(t)= \delta\psi(r_s,t)$ determines the amplitude
 and phase of the reconnected helical magnetic flux at the resonant surface, whereas the complex quantity\,\cite{rf1993}
 \begin{equation}
{\mit\Delta\Psi}_s = \left[r\,\frac{\partial \delta\psi}{\partial r}\right]_{r_{s-}}^{r_{s+}}
\end{equation}
parameterizes the amplitude and phase of the helical current sheet flowing at the surface. The solution of
the cylindrical tearing mode equation in the outer region, in the presence of an externally generated, resonant magnetic perturbation 
of the same helicity as the tearing mode, leads to the relation\,\cite{rf1993,fkr}
\begin{equation}\label{e110}
{\mit\Delta\Psi}_s= ({\mit\Delta}_s')\,{\mit\Psi}_s + (-{\mit\Delta}_s')\,{\mit\Psi}_v,
\end{equation}
where ${\mit\Delta}_s'$ is a real dimensionless quantity known as the {\em tearing stability index}. Moreover,
${\mit\Psi}_v$ is the so-called {\em vacuum flux}, and is defined as the reconnected magnetic flux
that would be driven at the resonant surface by the resonant magnetic perturbation were the
plasma intrinsically tearing stable (i.e., ${\mit\Delta}_s' <0$), and were there no current sheet at the resonant surface
(i.e., ${\mit\Delta\Psi}_s=0$).

@@

\subsection{Fundamental Equations}
The four-field model takes the form:\cite{fw}
\begin{align}
\frac{\partial\psi}{\partial\hat{t}}&= [\phi,\psi] -\tau_e\,(1+\lambda_e)\,[N,\psi]
+\hat{\eta}_\parallel\,J + \hat{E}_\parallel,\\[0.5ex]
\frac{\partial \hat{\nabla}^2\phi}{\partial \hat{t}}&= [\phi,\hat{\nabla}^2\phi] - \frac{\tau_i}{2}\left(\hat{\nabla}^2[\phi,N] + [\hat{\nabla}^2\phi,N] + [\hat{\nabla}^2 N,\phi]\right) + [J,\psi] \nonumber\\[0.5ex]&\phantom{=}+\hat{\chi}_\varphi  \,\hat{\nabla}^4\!\left(\phi + \tau_i\,N\right), \\[0.5ex]
\frac{\partial N}{\partial \hat{t}}&= [\phi,N] +c_\beta^{\,2}\,[V,\psi] +\hat{d}_\beta^{\,2}\,[J,\psi]
+ \hat{D}_\perp\,\hat{\nabla}_\perp^{\,2}N,\\[0.5ex]
\frac{\partial V}{\partial\hat{t}}&= [\phi,V] +[N,\psi] + \hat{\chi}_\varphi\,\hat{\nabla}^2 V.\label{e21}
\end{align}
Here, $[A,B]\equiv \hat{\nabla} A\times \hat{\nabla} B\cdot {\bf n}$, $\tau_e=[\tau/(1+\tau)]$, $\tau_i=1/(1+\tau)$, $\hat{t} = t/(r_s/V_A)$, $\hat{\eta}_{\parallel,\perp} = \eta_{\parallel,\perp}/(\mu_0\,r_s\,V_A)$, $\hat{E}_\parallel = E_\parallel/(B_z\,V_A)$, 
$\hat{\chi}_\varphi= \chi_\varphi/(r_s\,V_A)$, where $\eta_{\parallel,\perp}$ is the parallel/perpendicular plasma electrical
resistivity at the resonant surface, $E_\parallel$ the parallel inductive electric field that maintains the equilibrium toroidal
plasma current in the vicinity of the resonant surface, and $\chi_\varphi$  the anomalous perpendicular ion momentum
diffusivity at the resonant surface. 
Moreover, $d_\beta=c_\beta\,d_i$, and $\hat{d}_\beta=d_\beta/r_s$, where $c_\beta = \sqrt{\beta/(1+\beta)}$, and
$\beta=(5/3)\,\mu_0\,p_0/B_z^{\,2}$. Here, $d_\beta$ is usually referred to as the {\em ion sound radius}. Furthermore,
$\lambda_e=0.71\,\eta_e/(1+\eta_e)$ originates from the thermal force. Finally,\cite{fw}
\begin{equation}
\hat{D}_\perp \equiv \frac{D_{\perp}}{r_s\,V_A}= c_\beta^{\,2}\,\hat{\eta}_\perp +  \frac{2}{3}\left(1-c_\beta^{\,2}\right)\!\left(\frac{\eta_e\,\tau_e}{1+\eta_e}\,\hat{\chi}_{\perp\,e} + \frac{\eta_i\,\tau_i}{1+\eta_i}\,\hat{\chi}_{\perp\,i}\right),
\end{equation}
where $\hat{\chi}_{\perp\,e,i}=\chi_{\perp\,e,i}/(r_s\,V_A)$, and $\chi_{\perp\,e,i}$ is the (anomalous)
perpendicular electron/ion  energy diffusivity in the vicinity of the resonant surface. 
Note that Cole \& Fitzpatrick (2006) neglects the contribution of $\chi_{\perp\,e,i}$ to the perpendicular particle
diffusivity, $D_\perp$, leading to an anomalously small estimate for $D_\perp$. It is this deficiency that we aim to
correct in the present paper. To be more exact, given that $c_\beta\ll 1$ in conventional tokamak plasmas, and
that $\hat{\eta}_\perp\ll \hat{\chi}_{\perp\,e,i}$ (i.e., magnetic flux typically diffuses  across magnetic flux surfaces in tokamak plasmas much more
slowly than energy), the neglect of the terms involving $\hat{\chi}_{\perp\,e,i}$ in the previous equation leads to the
erroneous conclusion that $\hat{D}_\perp\ll \hat{\chi}_{\perp\,e,i}$ (i.e., particles diffuse across magnetic flux-surfaces in tokamak plasmas 
much more slowly than energy). The inclusion of the terms leads to the correct conclusion that  $\hat{D}_\perp\sim \hat{\chi}_{\perp\,e,i}$ (i.e., particles diffuse across magnetic flux-surfaces 
at a similar rate to energy).

@@

\subsection{Derivation of Linear Layer Equations}
In accordance with Eqs.~(\ref{e23})--(\ref{e28}), let us write
\begin{align}\label{e31}
\psi(\hat{x},\zeta,\hat{t}) &= \frac{\hat{x}^{\,2} }{2\,\hat{L}_s}+ \tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
\phi(\hat{x},\zeta,\hat{t}) &=-\hat{V}_E\,\hat{x}+ \tilde{\phi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
N(\hat{x},\zeta,\hat{t}) &= -\hat{V}_\ast\,\hat{x}+\tau_e\,\tilde{N}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
V(\hat{x},\zeta,\hat{t}) &= \hat{V}_\parallel +\tau_e\,\tilde{V}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\\[0.5ex]
J(\hat{x},\zeta,\hat{t}) &=-\left(\frac{2}{s_s}-1\right)\!\frac{1}{\hat{L}_s}+ \hat{\nabla}^2\tilde{\psi}(\hat{x})\,{\rm e}^{\,{\rm i}\,(\zeta-\hat{\omega}\,\hat{t})},\label{e36}
\end{align}
where $\zeta=m\,\theta-n\,\varphi$, $\hat{\omega}=r_s\,\omega/V_A$, and $\omega$ is the frequency of the tearing mode in the laboratory frame. 
Substituting Eqs.~(\ref{e31})--(\ref{e36}) into Eqs.~(\ref{e16})--(\ref{e21}), 
 and only retaining terms that
are first order in perturbed quantities, we obtain the following set of linear equations:
\begin{align}\label{e37}
-{\rm i}\,[\omega-\omega_E -(1+\lambda_e)\,\omega_{\ast\,e}]\,\tau_H\,\tilde{\psi} &= -{\rm i} \,\hat{x}\,[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}] + S^{-1}\,\hat{\nabla}^2\tilde{\psi},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E-\omega_{\ast\,i})\,\tau_H\,\hat{\nabla}^2\tilde{\phi} &= -{\rm i}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}+S^{-1}\,P_\varphi\,\hat{\nabla}^4\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{N} &= -{\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\phi}-{\rm i}\,c_\beta^{\,2}\,\hat{x}\,\tilde{V} - {\rm i}\,\tau_e\,\hat{d}_\beta^{\,2}\,\hat{x}\,\hat{\nabla}^2\tilde{\psi}\nonumber\\[0.5ex]
&\phantom{=} + S^{-1}\,P_\perp\,\hat{\nabla}_\perp^2 \tilde{N},\\[0.5ex]
-{\rm i}\,(\omega-\omega_E)\,\tau_H\,\tilde{V} &= {\rm i}\,\omega_{\ast\,e}\,\tau_H\,\tilde{\psi} - {\rm i}\,\hat{x}\,\tilde{N}
+ S^{-1}\,P_\varphi\,\hat{\nabla}^2\tilde{V}.\label{e40}
\end{align}
Here, 
$\tau_H = L_s/(m\,V_A)$ 
is the  hydromagnetic time, 
$\omega_E =(m/r_s)\,V_E(r_s)$
  the 
 ${\bf E}\times {\bf B}$ frequency, 
$\omega_{\ast\,e} = -\tau_e\,(m/r_s)V_\ast(r_s)$
the 
   electron diamagnetic
frequency,
$\omega_{\ast\,i} =\tau_i\,(m/r_s)V_\ast(r_s)$
 the  ion diamagnetic
frequency, 
$S=\tau_R/\tau_H$
 the  Lundquist number, 
$\tau_R = \mu_0\,r_s^{\,2}/\eta_\parallel$
 the
 resistive diffusion time, 
$\tau_\varphi
= r_s^{\,2}/\chi_\varphi$
the  toroidal momentum confinement time, and 
$\tau_\perp = r_s^{\,2}/D_\perp$.
  Furthermore, $P_\varphi = \tau_R/\tau_\varphi$ and $P_\perp = \tau_R/\tau_\perp$ are magnetic Prandtl numbers.

 Let us define the stretched radial variable $X = S^{1/3}\,\hat{x}$.
Assuming that $X\sim{\cal O}(1)$ in the layer (i.e., assuming that the layer thickness is roughly of order $S^{-1/3}\,r_s$),
and making use of the fact that $S\gg 1$ in conventional tokamak plasmas,  Eqs.~(\ref{e37})--(\ref{e40}) reduce to the following
set of linear layer equations:\,\cite{cole}
\begin{align}\label{e43}
-{\rm i}\,[Q-Q_E-(1+\lambda_e)\,Q_{e}]\,\tilde{\psi}&= - {\rm i}\,X\left[\tilde{\phi}-(1+\lambda_e)\,\tilde{N}\right] + \frac{d^{\,2}\tilde{\psi}}{d X^2},\\[0.5ex]
-{\rm i}\,(Q-Q_E -Q_{i})\,\frac{d^{\,2}\tilde{\phi}}{dX^2}&= - {\rm i}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^2}+ P_\varphi\,\frac{d^{\,4}}{dX^4}\!\left(\tilde{\phi} + \frac{\tilde{N}}{\tau}\right),\\[0.5ex]
-{\rm i}\,(Q-Q_E)\tilde{N} &= - {\rm i}\,Q_{e}\,\tilde{\phi} - {\rm i}\,c_\beta^{\,2}\,X\,\tilde{V}  - {\rm i} \,D^{2}\,X\,\frac{d^{\,2}\tilde{\psi}}{dX^{2}}
+ P_\perp\,\frac{d^{\,2} \tilde{N}}{dX^{2}},\\[0.5ex]
 -{\rm i}\,(Q-Q_E)\,\tilde{V} &= {\rm i}\,Q_{e}\,\tilde{\psi} - {\rm i}\,X\,\tilde{N} + P_\varphi\,\frac{d^{\,2}\tilde{V}}{dX^{2}}.\label{e46}
\end{align}
Here, $Q=S^{\,1/3}\,\omega\,\tau_H$, $Q_E = S^{\,1/3}\,\omega_E\,\tau_H$, $Q_{e,i} = S^{\,1/3}\,\omega_{\ast\,e,i}\,\tau_H$,
and $D = S^{\,1/3}\,\tau_e^{1/2}\,\hat{d}_\beta$.

\subsection{Asymptotic Matching}
The  linear layer equations, (\ref{e43})--(\ref{e46}), possess tearing parity solutions
characterized by the symmetry $\tilde{\psi}(-X)=\tilde\psi(X)$, $\tilde{\phi}(-X)=-\tilde{\phi}(X)$, 
$\tilde{N}(-X)= - \tilde{N}(X)$, $\tilde{V}(-X)=\tilde{V}(X)$. If we assume that
the asymptotic behavior of the tearing parity layer solutions is such that 
\begin{equation}\label{e47}
\tilde{\psi}\rightarrow  \psi_0\!\left[1+ \frac{\hat{\mit\Delta}}{2}\,|X| + {\cal O}(X^2)\right]
\end{equation}
as $|X|\rightarrow\infty$, where $\psi_0$ is an arbitrary constant, then asymptotic matching to the outer solution yields
\begin{equation}\label{e48}
{\mit\Delta\Psi}_s= (S^{1/3}\,\hat{\mit\Delta})\,\,{\mit\Psi}_s.
\end{equation}

@@

\bibitem{yush} P.N.~Yushmanov, T.~Takizuka, K.S.~Reidel, O.J.W.F.~Kardaun, J.G.~Cordey, S.M.~Kaye,
and D.E.~Post, Nucl.\ Fusion {\bf 30}, 1999 (1990).

\bibitem{logan} N.C.~Logan, J.-K.~Park, Q.~Hu, C.~Paz-Soldan, T.~Markovic, H.~Wang,
Y.~In, L.~Piron, P.~Piovesan, C.E.~Myers, et al., Nucl.\ Fusion {\bf 60}, 086010 (2020).
